Categorical Predictor Embeddings and Attention Based Neural Networks in Actuarial Modeling

### 2021-04-07 manuscript/manuscript.Rmd
Update manuscript.Rmd

---
title: Categorical Predictor Embeddings and Attention Based Neural Networks in Actuarial Modeling
authors:
  - name: Kevin Kuo 
    affiliation: RStudio and Kasa AI
    email: kevin@kasa.ai
  - name: Ronald Richman
    affiliation: QED Actuaries and Consultants
    email: ronaldrichman@gmail.com
abstract: |
  Enter the text of your abstract here.
keywords:
  - categorical data
  - neural networks
  - embeddings
  - attention
  - severity modelling
  - National Flood Insurance Program 
bibliography: references.bib
output:
  bookdown::pdf_book:
    base_format: rticles::arxiv_article
header-includes: |
    \usepackage{amsmath}
    \usepackage{mathtools}
    \usepackage{bm}
    \usepackage{bbm}
    \usepackage{float}
    \DeclarePairedDelimiter\ceil{\lceil}{\rceil}
    \newcommand{\norm}[1]{\| #1 \|}
---

@@

Categorical data are modelled by actuaries in many different contexts, from pricing of insurance products to reserving 
for the liabilities generated by these products. Sometimes, these data are modelled in an explicit manner, for example, 
when building models that apply across multiple categories, a form of dummy coding is usually used. For example, when 
building models to price the frequency of motor insurance claims, claim experience relating to different types of motor
vehicle will often be modelled by including a (single) factor within models that modifies the relative frequency 
predicted for each type of vehicle. In other cases, modelling is performed for each category separately, thus the 
categorical data is used within the modelling in an implicit manner, for example, common practice is to estimate 
reserves for different lines of business separately, meaning to say, with no parameters being shared across each of the
reserving models.

@@

This approach to modelling categorical data has several advantages over more traditional treatments of categorical data.
Using categorical embeddings instead of traditional techniques has been shown to increase predictive accuracy of 
models, for example, see @Richman2018 in the context of pricing. Models incorporating categorical embeddings can be
pre-calibrated to traditional actuarial models, increasing the speed with which these models can be calibrated and 
leading to models with better explainability [@wuthrich2019yes]. Finally, the similarity between the vectors learned 
for different categories can be inspected, sometimes leading to insights into the workings of models, see, for example,
@Kuo2019.

On the other hand, several open questions about the use of embeddings within actuarial work remain, which we aim to 
address in this study. First, hyperparameter settings for embeddings, such as the dimensions of the embedding layer and
the use of regularization techniques such as dropout or normalization, that achieve optimal predictive performance has
not yet been studied in detail in the actuarial literature. In this work, we aim to study how embeddings using 
different settings perform in the context of a large-scale predictive modelling problem, and give guidance on the 
process that can be followed to determine this in other problems. Although neural network have been shown to achieve
excellent predictive accuracy on actuarial tasks, many actuaries still prefer to use GLM models for pricing tasks, 
thus, the issue of whether transferring embeddings to GLM models can achieve better performance is considered in this
paper. <!-- Traditional actuarial techniques such as credibility theory have been used to work with some types of categorical data, but no study has been -->
<!-- performed whether this can be applied within embeddings; here, we investigate whether performance is enhanced by applying credibility theory on embeddings 
relating to categorical variables with many labels. Whereas embedding layers are usually considered in the context of categorical data,the 
option exists to quantize numerical data and model it using embeddings, however, the results of doing so have not been investigated. -->
Finally, in the past several years, a new type of neural network architecture based on attention [@Vaswani2017] has
been successfully used on embeddings in the field of natural language processing and we incorporate attention 
based models into our predictive modelling example to demonstrate the use of these models for actuarial purposes.

@@

The rest of this manuscript is organized as follows. Section \ref{lit_review} reviews recent applications of embeddings
in the actuarial literature. Section \ref{defns} provides the notation used in the paper and defines GLMs, neural 
networks and related modelling concepts, including embeddings and attention. In Section \ref{modelling}, we provide 
initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural 
network model. That section also considers how successfully the embeddings used in the neural network model can be 
transferred to a GLM model of the same data and how learned embeddings can be interpreted. We focus on attention based models 
in Section \ref{attention_models}. Finally, Section \ref{Conclusions} provides a discussion of the results of this paper
and considers avenues for future research.

@@

A different approach to modelling categorical data is credibility theory (see @Buhlmann2006 for an overview), which, 
in the context of rating, can be applied to derive premiums that reflect the experience of a particular policyholder, by 
estimating premiums as a weighted average between the premium produced using the collective experience (i.e. of all 
policyholders) and the premium produced using the experience of the particular policyholder. The weight used in this 
average is called a credibility factor and is calculated with reference to te variability of the policyholder experience 
relative to the variability of the group experience. In this context, the implicit categorical variable is the 
policyholder under consideration.

Generalized Linear Mixed Models (GLMMs) are an extension of GLMs that are designed for modelling categorical data using 
a principle very similar to that of credibility theory [@Klinker2010]. Instead of calibrating indicator variables for 
each level of the category, GLMMs estimate effects for each of these levels as a combination of the overall group mean 
and the experience in each level of the category.

Embedding layers represent a different approach to the problem of modelling categorical data that was recently 
introduced in an actuarial context. Note that in the next section, we reflect on similarities between the conventional 
approaches discussed above and embedding layers. @Richman2018 reviewed the concept of embedding layers and connected 
the sharing of information across categories to the familiar concept of credibility theory. In that work, two 
applications of embedding layers were demonstrated. The first of these was in a Property and Casualty (P&C) pricing 
context, it was shown that the out-of-sample accuracy of a neural network trained to predict claims frequencies on motor 
third party liability was enhanced by modelling the categorical variables within this dataset using embedding layers. 
Second, a neural network with embedding layers was used to model all of the mortality rates in the Human Mortality 
Database, where the differences in population mortality across countries and the differences in mortality at different 
ages were modelled with embedding layers, again producing more accurate out of sample performance than the other models 
tested.

@@

In this study, we are concerned with regression modelling, which is the task of predicting an unknown outcome $y$ on the 
basis of information about that outcome contained in predictor variables, or features, stored in a matrix $X$. For 
simplicity, we only consider the case of univariate outcomes, i.e., $y \in \mathbb{R}^1$. The outcomes and the rows of 
the predictor variable matrix are indexed by $i \in \{1 \dots I\}$, where $i$ represents a particular observation of 
$(y_i, \mathbf{x}_i)$, where bold indicates that we are now dealing with a vector. The columns of the predictor 
variables are indexed by $j \in \{1 \dots J\}$, where $j$ represents a particular predictor variable, of which $J$ have 
been observed, thus, we use the notation $X_j$ to represent the $j$th predictor variable and $X \in \mathbb{R}^J$. 
Formally, we look to build regression models that map from the predictor variables $\mathbf{x}_i$ to the outcome $y$ 
using a function $f$ of the form:

@@

Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to RNNs [@Bahdanau2015a] 
and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], 
and, more recently, has been applied to computer vision and tabular modelling tasks. 
Attention mechanisms allow deep neural nets to weight the covariates entering the model in a flexible manner; these types of applications in natural language 
processing are demonstrated in,
for example, @Vaswani2017a. In an actuarial context, attention mechanisms can be understood as giving greater weight to covariates that are important for the modelling task. 
In this section we provide a theoretical introduction to attention mechanisms and then discuss applications of attention to modeling tabular data. 
In the following sections of this paper, we then consider whether adding attention to an model that uses embeddings can provide better predictive accuracy. 
The following is intended as a high level review of some of the relevant theory behind attention based approaches; for more technical details the sources quoted in this section can be consulted.

@@

```{=latex}
\begin{equation}
X^*: \mathbb{R}^{(q \times d) \times (q \times d) \times (q \times d)} \to \mathbb{R}^{(q \times d)}, ~~
(Q, K, X') ~\mapsto ~ X^* = A(Q, K, X'),
\label{eq:attention}
\end{equation}
```
where $Q \in \mathbb{R}^{q \times d}$ is a matrix of query vectors, $K \in \mathbb{R}^{q \times d}$ is a matrix of key vectors,
 $X' \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $X^* \in \mathbb{R}^{q \times d}$, 
 the output of the attention mechanism, is a new matrix of values that have been reweighted according to their importance for the modelling problem. 
 As noted above, several different options for the mapping in Equation \ref{eq:attention} exist in the literature; here we describe the scaled dot-product self-attention mechanism 
 used in @Vaswani2017a. In more detail, consider that $X'$ is a matrix of covariates relating to a regression problem, which, 
 in the case of tabular data, will usually be composed of embeddings of the same dimension for several different categorical or numerical variables.
 In the case discussed here we have $q$ covariates mapped to embeddings of dimension $d$. For clarity, note that in Equation \ref{eq:embed_to_nn} 
 we have used the symbol $X'$ to denote the vector of embeddings and numerical inputs which is passed into the neural network. 
 We slightly overload this notation and, in what follows, we now use the symbol $X'$ to refer to the matrix of embeddings of dimension $q \times d$.

@@

An intuitive explanation of the attention formula is as follows: we start by considering the importance of all of the covariates 
that we have for our modelling problem in the context of each individual covariate. This is done by assigning a score between zero
and one to each covariate in the modelling problem, and we repeat this process for each of the covariates. Then, we replace each 
of the original covariates with a new covariate that has been formed by taking a weighted average of the covariates and the scores.

@@

### Attention Modelling for Tabular Data

Several different approaches to applying attention within the modelling of tabular data have been proposed in the literature. Perhaps the simplest way of doing 
this is to insert an attention layer between the embeddings and the rest of the neural network. Mathematically, we can modify Equation \ref{eq:embed_to_nn} as follows:

@@

Finally, a different way of incorporating attention into the modeling of tabular data has been proposed by @Ark2019, who refer to their model as TabNet. 
In summary, the main idea of the TabNet model is to try emulate the excellent performance of decision trees on tabular data modelling using deep neural networks. 
This is done by structuring the neural networks to emulate a key aspect of decision tree modelling, which is the efficient selection of relevant covariates
for the model task. Within TabNet, an attention based model is used to select features by estimating attention scores for each covariate within $X$. 
The covariates are multiplied by the attention scores to down-weight less relevant features for the prediction problem. Other less important details of the TabNet
model are given in @Ark2019.

# Predictive Modeling with Embeddings {#modelling}

@@

Investigate approaches for using embedding layers for numeric variables, or numeric variables that were captured as 
categorical variables (Can the modelling of numerical variables benefit from the application of embedding layers?) How 
should this best be done? CatBoost - cut into 256 groups smoothness Map numeric to a dense layer and use that as 
embedding - basis expansion Add a distribution to the embeddings Can insights from credibility theory lead to enhanced embeddings? Take credibility mixture over embeddings Cluster embeddings PCA of embeddings
-->
# Attention based modelling {#attention_models}
In this section we investigate whether the predictive performance of the models applied to the NFIP dataset can be improved
by applying the attention based models defined in Section \ref{attention}. We discuss the implementation of each of the 
Simple Attention, TabTransformer and TabNet models in the following sub-section, then discuss how the modifications made
to the embeddings through the application of attention can be visualized in the following sub-section. We conclude the 
section with a discussion of the model results.

@@

Compared to the models presented in the previous section, the models presented here are closer to state of the art models that
might be used for tabular data modelling problems. To the best of our knowledge, this is the first analysis of these architectures
within the actuarial literature.

@@

```{r nn-3, echo = FALSE, fig.cap = "Architecture of Model 6.", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/tabt.pdf")
```
### Model 7: TabNet
The final model we consider in this subsection is the TabNet architecture. The structure of the model is quite similar to Model 6, except 
that a more specialized form of self-attention is used to select the most important covariates for the modelling problem.

@@

In Table \@ref(tab:cv-results-attn), we show the cross-validated performance metrics of each of the models, 
as well as the two best performing models from the previous section. As before, we report both the root mean squared error (RMSE) 
and the mean absolute error (MAE). The results show that Model 5, which simply adds attention to Model 4, outperforms Model 4 on both the RMSE and 
MAE metrics. Thus, there is some room to argue that for tabular data modelling that uses embeddings for categorical data, 
the use of attention within models should be considered. Disappointingly, the TabNet architecture performs poorly, perhaps due to insufficient hyperparameter tuning, 
but indicating that ``out of the box", TabNet does not appear to work well for this modelling task. Finally, the TabTransformer model shows the best performance of all
 models considered in this research, beating the other models by a significant margin on both the RMSE and MAE metrics.

@@

```{r embdexp, echo = FALSE, fig.cap = "Embedding versus Contextual Embedding, Flood Zone, first PCA components, points coloured based on crawl space variable", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/emb_vs_cembd_exp.pdf")
```
To investigate the predictive value added by the contextual embeddings, a simple Gamma GLM was fit to these 10 000 observations, with the goal of predicting the 
claim amount based only on either the embeddings or the contextual embeddings. As shown in Table \@ref(tab:emd-vs-cembd), the performance of the latter model, 
as indicated by the Aikaike Information Criterion (AIC) was significantly better than the latter model (37 129 compared with 37 463), 
in other words, the contextual embeddings that incorporate information across all of the categorical variables are significantly better predictors 
of claim severity compared with the embeddings.

Table: (\#tab:emd-vs-cembd) AIC for GLMs predicting claim severity, embeddings compared with contextual embeddings.

|Embedding Type       |      AIC|
|:--------------------|--------:|
|Embedding            | 37,464|
|Contextual embedding | 37,129|

@@

This study has focused on how embeddings can be applied within the context of actuarial modelling, by illustrating a range of approaches: first, relatively simple
neural networks with embeddings were defined, the embeddings from these models were reused within traditional GLM models and, finally, more advanced attention based models 
were studied. These models were demonstrated within the context of a claims severity modelling problem based on data from the NFIP. Whereas we have only considered severity 
in this study, it is likely that our findings will replicate for the modelling of claim frequency, which is usually an easier problem. Our key findings are that 
processing categorical variables with multi-dimensional embeddings leads to enhanced performance within simple neural networks, and that, by including these within traditional
GLM models, the predictive performance of these models can be enhanced, compared to the usual encoding scheme for categorical variables. Some of the attention based models 
considered within this study performed well, in particular, the TabTransformer model of @Huang2020 appears quite promising for use in actuarial modelling. The study has also 
illustrated how embeddings can be visualized using the PCA and t-SNE techniques. We found that, in the case of the NFIP data, it is possible to explain which variables modify 
the embeddings based on the context of each observation.

Several avenues for future research can be considered. One surprising finding of our work is that the TabNet model performed quite poorly, leading us to conclude that this 
model appears to be less suitable for actuarial modelling. Understanding these findings in more detail would be a valuable contribution to the literature. Another helpful contribution
would be to investigate the optimal hyperparameters for the TabTransformer model in the context of actuarial modelling. Finally, extneding our findings to a claims frequency example
could be considered.

>>>>

---
title: Categorical Predictor Embeddings and Attention Based Neural Networks in Actuarial Modeling
authors:
  - name: Kevin Kuo 
    affiliation: RStudio and Kasa AI
    email: kevin@kasa.ai
  - name: Ronald Richman
    affiliation: QED Actuaries and Consultants
    email: ronaldrichman@gmail.com
abstract: |
  Enter the text of your abstract here.
keywords:
  - categorical data
  - neural networks
  - embeddings
  - attention
  - severity Modeling
  - National Flood Insurance Program 
bibliography: references.bib
output:
  bookdown::pdf_book:
    base_format: rticles::arxiv_article
header-includes: |
    \usepackage{amsmath}
    \usepackage{mathtools}
    \usepackage{bm}
    \usepackage{bbm}
    \usepackage{float}
    \DeclarePairedDelimiter\ceil{\lceil}{\rceil}
    \newcommand{\norm}[1]{\| #1 \|}
---

@@

Categorical data are modelled by actuaries in many different contexts, from pricing of insurance products to reserving 
for the liabilities generated by these products. Sometimes, these data are modelled in an explicit manner, for example, 
when building models that apply across multiple categories, a form of dummy coding is usually used. For example, when 
building models to price the frequency of motor insurance claims, claim experience relating to different types of motor
vehicle will often be modelled by including a (single) factor within models that modifies the relative frequency 
predicted for each type of vehicle. In other cases, Modeling is performed for each category separately, thus the 
categorical data is used within the Modeling in an implicit manner, for example, common practice is to estimate 
reserves for different lines of business separately, meaning to say, with no parameters being shared across each of the
reserving models.

@@

This approach to Modeling categorical data has several advantages over more traditional treatments of categorical data.
Using categorical embeddings instead of traditional techniques has been shown to increase predictive accuracy of 
models, for example, see @Richman2018 in the context of pricing. Models incorporating categorical embeddings can be
pre-calibrated to traditional actuarial models, increasing the speed with which these models can be calibrated and 
leading to models with better explainability [@wuthrich2019yes]. Finally, the similarity between the vectors learned 
for different categories can be inspected, sometimes leading to insights into the workings of models, see, for example,
@Kuo2019.

On the other hand, several open questions about the use of embeddings within actuarial work remain, which we aim to 
address in this study. First, hyperparameter settings for embeddings, such as the dimensions of the embedding layer and
the use of regularization techniques such as dropout or normalization, that achieve optimal predictive performance has
not yet been studied in detail in the actuarial literature. In this work, we aim to study how embeddings using 
different settings perform in the context of a large-scale predictive Modeling problem, and give guidance on the 
process that can be followed to determine this in other problems. Although neural network have been shown to achieve
excellent predictive accuracy on actuarial tasks, many actuaries still prefer to use GLM models for pricing tasks, 
thus, the issue of whether transferring embeddings to GLM models can achieve better performance is considered in this
paper. <!-- Traditional actuarial techniques such as credibility theory have been used to work with some types of categorical data, but no study has been -->
<!-- performed whether this can be applied within embeddings; here, we investigate whether performance is enhanced by applying credibility theory on embeddings 
relating to categorical variables with many labels. Whereas embedding layers are usually considered in the context of categorical data,the 
option exists to quantize numerical data and model it using embeddings, however, the results of doing so have not been investigated. -->
Finally, in the past several years, a new type of neural network architecture based on attention [@Vaswani2017] has
been successfully used on embeddings in the field of natural language processing and we incorporate attention 
based models into our predictive Modeling example to demonstrate the use of these models for actuarial purposes.

@@

The rest of this manuscript is organized as follows. Section \ref{lit_review} reviews recent applications of embeddings
in the actuarial literature. Section \ref{defns} provides the notation used in the paper and defines GLMs, neural 
networks and related Modeling concepts, including embeddings and attention. In Section \ref{Modeling}, we provide 
initial models for the NFIP dataset and consider the influence of hyperparameter choices on the results of the neural 
network model. That section also considers how successfully the embeddings used in the neural network model can be 
transferred to a GLM model of the same data and how learned embeddings can be interpreted. We focus on attention based models 
in Section \ref{attention_models}. Finally, Section \ref{Conclusions} provides a discussion of the results of this paper
and considers avenues for future research.

@@

A different approach to Modeling categorical data is credibility theory (see @Buhlmann2006 for an overview), which, 
in the context of rating, can be applied to derive premiums that reflect the experience of a particular policyholder, by 
estimating premiums as a weighted average between the premium produced using the collective experience (i.e. of all 
policyholders) and the premium produced using the experience of the particular policyholder. The weight used in this 
average is called a credibility factor and is calculated with reference to te variability of the policyholder experience 
relative to the variability of the group experience. In this context, the implicit categorical variable is the 
policyholder under consideration.

Generalized Linear Mixed Models (GLMMs) are an extension of GLMs that are designed for Modeling categorical data using 
a principle very similar to that of credibility theory [@Klinker2010]. Instead of calibrating indicator variables for 
each level of the category, GLMMs estimate effects for each of these levels as a combination of the overall group mean 
and the experience in each level of the category.

Embedding layers represent a different approach to the problem of Modeling categorical data that was recently 
introduced in an actuarial context. Note that in the next section, we reflect on similarities between the conventional 
approaches discussed above and embedding layers. @Richman2018 reviewed the concept of embedding layers and connected 
the sharing of information across categories to the familiar concept of credibility theory. In that work, two 
applications of embedding layers were demonstrated. The first of these was in a Property and Casualty (P&C) pricing 
context, it was shown that the out-of-sample accuracy of a neural network trained to predict claims frequencies on motor 
third party liability was enhanced by Modeling the categorical variables within this dataset using embedding layers. 
Second, a neural network with embedding layers was used to model all of the mortality rates in the Human Mortality 
Database, where the differences in population mortality across countries and the differences in mortality at different 
ages were modelled with embedding layers, again producing more accurate out of sample performance than the other models 
tested.

@@

In this study, we are concerned with regression Modeling, which is the task of predicting an unknown outcome $y$ on the 
basis of information about that outcome contained in predictor variables, or features, stored in a matrix $X$. For 
simplicity, we only consider the case of univariate outcomes, i.e., $y \in \mathbb{R}^1$. The outcomes and the rows of 
the predictor variable matrix are indexed by $i \in \{1 \dots I\}$, where $i$ represents a particular observation of 
$(y_i, \mathbf{x}_i)$, where bold indicates that we are now dealing with a vector. The columns of the predictor 
variables are indexed by $j \in \{1 \dots J\}$, where $j$ represents a particular predictor variable, of which $J$ have 
been observed, thus, we use the notation $X_j$ to represent the $j$th predictor variable and $X \in \mathbb{R}^J$. 
Formally, we look to build regression models that map from the predictor variables $\mathbf{x}_i$ to the outcome $y$ 
using a function $f$ of the form:

@@

Attention mechanisms have been widely applied within the deep learning literature to give more flexibility to RNNs [@Bahdanau2015a] 
and subsequently as a replacement for FCNs in the so-called Transformer architecture, which is now widely used in natural language processing [@Vaswani2017a], 
and, more recently, has been applied to computer vision and tabular Modeling tasks. 
Attention mechanisms allow deep neural nets to weight the covariates entering the model in a flexible manner; these types of applications in natural language 
processing are demonstrated in,
for example, @Vaswani2017a. In an actuarial context, attention mechanisms can be understood as giving greater weight to covariates that are important for the Modeling task. 
In this section we provide a theoretical introduction to attention mechanisms and then discuss applications of attention to modeling tabular data. 
In the following sections of this paper, we then consider whether adding attention to an model that uses embeddings can provide better predictive accuracy. 
The following is intended as a high level review of some of the relevant theory behind attention based approaches; for more technical details the sources quoted in this section can be consulted.

@@

```{=latex}
\begin{equation}
X^*: \mathbb{R}^{(q \times d) \times (q \times d) \times (q \times d)} \to \mathbb{R}^{(q \times d)}, ~~
(Q, K, X') ~\mapsto ~ X^* = Attn(Q, K, X'),
\label{eq:attention}
\end{equation}
```
where $Q \in \mathbb{R}^{q \times d}$ is a matrix of query vectors, $K \in \mathbb{R}^{q \times d}$ is a matrix of key vectors,
 $X' \in \mathbb{R}^{q \times d}$ is a matrix of value vectors and $X^* \in \mathbb{R}^{q \times d}$, 
 the output of the attention mechanism, is a new matrix of values that have been reweighted according to their importance for the Modeling problem. 
 As noted above, several different options for the mapping in Equation \ref{eq:attention} exist in the literature; here we describe the scaled dot-product self-attention mechanism 
 used in @Vaswani2017a. In more detail, consider that $X'$ is a matrix of covariates relating to a regression problem, which, 
 in the case of tabular data, will usually be composed of embeddings of the same dimension for several different categorical or numerical variables.
 In the case discussed here we have $q$ covariates mapped to embeddings of dimension $d$. For clarity, note that in Equation \ref{eq:embed_to_nn} 
 we have used the symbol $X'$ to denote the vector of embeddings and numerical inputs which is passed into the neural network. 
 We slightly overload this notation and, in what follows, we now use the symbol $X'$ to refer to the matrix of embeddings of dimension $q \times d$.

@@

An intuitive explanation of the attention formula is as follows: we start by considering the importance of all of the covariates 
that we have for our Modeling problem in the context of each individual covariate. This is done by assigning a score between zero
and one to each covariate in the Modeling problem, and we repeat this process for each of the covariates. Then, we replace each 
of the original covariates with a new covariate that has been formed by taking a weighted average of the covariates and the scores.

@@

### Attention Modeling for Tabular Data

Several different approaches to applying attention within the Modeling of tabular data have been proposed in the literature. Perhaps the simplest way of doing 
this is to insert an attention layer between the embeddings and the rest of the neural network. Mathematically, we can modify Equation \ref{eq:embed_to_nn} as follows:

@@

Finally, a different way of incorporating attention into the modeling of tabular data has been proposed by @Ark2019, who refer to their model as TabNet. 
In summary, the main idea of the TabNet model is to try emulate the excellent performance of decision trees on tabular data Modeling using deep neural networks. 
This is done by structuring the neural networks to emulate a key aspect of decision tree Modeling, which is the efficient selection of relevant covariates
for the model task. Within TabNet, an attention based model is used to select features by estimating attention scores for each covariate within $X$. 
The covariates are multiplied by the attention scores to down-weight less relevant features for the prediction problem. Other less important details of the TabNet
model are given in @Ark2019.

# Predictive Modeling with Embeddings {#Modeling}

@@

Investigate approaches for using embedding layers for numeric variables, or numeric variables that were captured as 
categorical variables (Can the Modeling of numerical variables benefit from the application of embedding layers?) How 
should this best be done? CatBoost - cut into 256 groups smoothness Map numeric to a dense layer and use that as 
embedding - basis expansion Add a distribution to the embeddings Can insights from credibility theory lead to enhanced embeddings? Take credibility mixture over embeddings Cluster embeddings PCA of embeddings
-->
# Attention based Modeling {#attention_models}
In this section we investigate whether the predictive performance of the models applied to the NFIP dataset can be improved
by applying the attention based models defined in Section \ref{attention}. We discuss the implementation of each of the 
Simple Attention, TabTransformer and TabNet models in the following sub-section, then discuss how the modifications made
to the embeddings through the application of attention can be visualized in the following sub-section. We conclude the 
section with a discussion of the model results.

@@

Compared to the models presented in the previous section, the models presented here are closer to state of the art models that
might be used for tabular data Modeling problems. To the best of our knowledge, this is the first analysis of these architectures
within the actuarial literature.

@@

```{r nn-3, echo = FALSE, fig.cap = "Architecture of Model 6.", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/tabt.pdf")
```
### Model 7: TabNet
The final model we consider in this subsection is the TabNet architecture. The structure of the model is quite similar to Model 6, except 
that a more specialized form of self-attention is used to select the most important covariates for the Modeling problem.

@@

In Table \@ref(tab:cv-results-attn), we show the cross-validated performance metrics of each of the models, 
as well as the two best performing models from the previous section. As before, we report both the root mean squared error (RMSE) 
and the mean absolute error (MAE). The results show that Model 5, which simply adds attention to Model 4, outperforms Model 4 on both the RMSE and 
MAE metrics. Thus, there is some room to argue that for tabular data Modeling that uses embeddings for categorical data, 
the use of attention within models should be considered. Disappointingly, the TabNet architecture performs poorly, perhaps due to insufficient hyperparameter tuning, 
but indicating that ``out of the box", TabNet does not appear to work well for this Modeling task. Finally, the TabTransformer model shows the best performance of all
 models considered in this research, beating the other models by a significant margin on both the RMSE and MAE metrics.

@@

```{r embdexp, echo = FALSE, fig.cap = "Embedding versus Contextual Embedding, Flood Zone, first PCA components, points coloured based on crawl space variable", out.width = "80%", fig.align = "center"}
knitr::include_graphics("images/emb_vs_cembd_exp.pdf")
```
To investigate the predictive value added by the contextual embeddings, a simple Gamma GLM was fit to these 10 000 observations, with the goal of predicting the 
claim amount based only on either the embeddings or the contextual embeddings. As shown in Table \@ref(tab:emd-vs-cembd), the performance of the latter model, 
as indicated by the RMSE and MAE metrics is significantly better, in other words, the contextual embeddings that incorporate information across all of the categorical variables are significantly better predictors 
of claim severity compared with the embeddings.

Table: (\#tab:emd-vs-cembd) RMSE and MAE for GLMs predicting claim severity, embeddings compared with contextual embeddings.

|Embedding Type       |     RMSE|      MAE|
|:--------------------|--------:|--------:|
|Embedding            | 62596.84| 40323.82|
|Contextual embedding | 62027.85| 39450.45|

@@

This study has focused on how embeddings can be applied within the context of actuarial Modeling, by illustrating a range of approaches: first, relatively simple
neural networks with embeddings were defined, the embeddings from these models were reused within traditional GLM models and, finally, more advanced attention based models 
were studied. These models were demonstrated within the context of a claims severity Modeling problem based on data from the NFIP. Whereas we have only considered severity 
in this study, it is likely that our findings will replicate for the Modeling of claim frequency, which is usually an easier problem. Our key findings are that 
processing categorical variables with multi-dimensional embeddings leads to enhanced performance within simple neural networks, and that, by including these within traditional
GLM models, the predictive performance of these models can be enhanced, compared to the usual encoding scheme for categorical variables. Some of the attention based models 
considered within this study performed well, in particular, the TabTransformer model of @Huang2020 appears quite promising for use in actuarial Modeling. The study has also 
illustrated how embeddings can be visualized using the PCA and t-SNE techniques. We found that, in the case of the NFIP data, it is possible to explain which variables modify 
the embeddings based on the context of each observation.

Several avenues for future research can be considered. One surprising finding of our work is that the TabNet model performed quite poorly, leading us to conclude that this 
model appears to be less suitable for actuarial Modeling. Understanding these findings in more detail would be a valuable contribution to the literature. Another helpful contribution
would be to investigate the optimal hyperparameters for the TabTransformer model in the context of actuarial Modeling. Finally, extending our findings to a claims frequency example
could be considered.
